---
title: "Communicate your Results with Rmarkdown"
author: "Otho Mantegazza"
output:
  word_document:
    reference_docx: templates/kjhealy-ref-mod2.docx
---


Proposal: [R-Ladies Milan](https://www.meetup.com/R-Ladies-Milan/) workshop, May 9^th^ (?), 2019.

# Abstract

In data science, we need to **communicate** our results and observations. R has powerful tools for communication, such as **Rmarkdown** and **knitr**.

In this workshop we will learn how to use those packages to knit together text and R code and create beautiful and reproducible *reports*, *slides* and *web pages*.

While working on plant science, I've been using these tools when I had to communicate to my team both results and methodology. 

In this workshop I'll bring both examples from my work and simple code snippets that you can try to run on your computer.

Level: beginner

Be sure that you have installed the packages Rmarkdown and knitr.

```{r, eval = FALSE}
install.packages(c("rmarkdown", "knitr"))
```

Additional packages that you might want to try:

```{r, eval = FALSE}
install.packages(c("revealjs","bookdown","blogdown","leaflet","r2d3"))
```